\textbf{Autoreduction - an automated data reduction system for beamline instruments at the ISIS Facility}

### 2017-07-11 Documentation/paper/paper.tex
Removed border around reference numbers

\usepackage[unicode=true]{hyperref}
\usepackage{enumitem}
\usepackage{graphicx,grffile}

@@

The purpose of the autoreduction system is to provide a useful automation
step in this process. The system described in this paper allows data coming 
off an instrument to be automatically reduced using a dedicated software package 
such as Mantid\cite{mantid}, whilst also lending transparency to the process and
letting users control it through a straightforward web interface.

Automated data reduction is a concept which is actively persued at other large facilities.
At the NOBUGS 2016 Conference\cite{NOBUGS}, there were several talks given by delegates
from other large scale facilities which mentioned the automated reduction of data at a variety
of facilities.

>>>>

\usepackage[unicode=true, hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{graphicx,grffile}
\usepackage{xcolor}
\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
}

@@

The purpose of the autoreduction system is to provide a useful automation
step in this process. The system described in this paper allows data coming 
off an instrument to be automatically reduced using a dedicated software package 
such as Mantid \cite{mantid}, whilst also lending transparency to the process and
letting users control it through a straightforward web interface.

Automated data reduction is a concept which is actively persued at other large facilities.
At the NOBUGS 2016 Conference \cite{NOBUGS}, there were several talks given by delegates
from other large scale facilities which mentioned the automated reduction of data at a variety
of facilities.
